Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-20 paper.qmd
Updated different b1 choices with fixed q

```{r}
#| label: hexbin-regular-scurve1
## hexagon binning to have regular hexagons
hb_obj_scurve1 <- hex_binning(
  data = umap_scurve_scaled, 
  bin1 = 7, 
  r2 = r2,
  q = 0.12)

a1_1 <- calc_bins_y(
  bin1 = 7, 
  r2 = r2,
  q = 0.12
)$a1

@@

```{r}
#| label: hexbin-regular-scurve2
## hexagon binning to have regular hexagons
hb_obj_scurve2 <- hex_binning(
  data = umap_scurve_scaled, 
  bin1 = 11, 
  r2 = r2,
  q = 0.07)

a1_2 <- calc_bins_y(
  bin1 = 11, 
  r2 = r2,
  q = 0.07
)$a1

@@

```{r}
#| label: hexbin-regular-scurve3
## hexagon binning to have regular hexagons
hb_obj_scurve3 <- hex_binning(
  data = umap_scurve_scaled, 
  bin1 = 17, 
  r2 = r2,
  q = 0.05)

a1_3 <- calc_bins_y(
  bin1 = 17, 
  r2 = r2,
  q = 0.05
)$a1

@@

effective_bin2_scurve <- calc_bins_y(
  bin1 = effective_bin1_scurve, 
  r2 = r2, 
  q = 0.07)$bin2

scurve_model <- fit_highd_model(
  training_data = training_data_scurve,
  emb_df = umap_scurve_scaled,
  bin1 = effective_bin1_scurve,
  r2 = r2,
  q = 0.07,
  is_bin_centroid = TRUE,
  is_rm_lwd_hex = FALSE,
  col_start_highd = "x"
)

@@

<!--To generate errors for different total number of bins-->
```{r}
#| label: bins-scurve
#| eval: false
## To initialize benchmark values to remove low density hexagons
benchmark_rm_hex_vec <- append(seq(0, 0.99, by=0.1), c(benchmark1, 0.99))

@@

```{r}
#| label: diff-bins-scurve-buff
## To initialize benchmark values to remove low density hexagons
benchmark_rm_hex_vec <- seq(0, 0.7, by=0.1)
bin1_vec_scurve <- c(7, 11, 17)
error_rm_scurve <- data.frame(matrix(nrow = 0, ncol = 0))

    a1 <- calc_bins_y(bin1 = xbins, r2 = r2, q = 0.07)$a1

    ## Compute error
    error_df <- glance(
      df_bin_centroids = df_bin_centroids_scurve_high_dens,
      df_bin = df_bin_scurve_high_dens,
      training_data = training_data_scurve,
      newdata = NULL,
      type_NLDR = "UMAP",
      col_start = "x") |>
      mutate(benchmark_rm_lwd = benchmark_rm_lwd,
             bin1 = xbins,
             b_non_empty = NROW(df_bin_centroids_scurve_high_dens))

mse_scurve_lwd <- ggplot(error_rm_scurve, 
                     aes(x = benchmark_rm_lwd, 
                         y = MSE,
                         colour = as.factor(bin1),
                         group = as.factor(bin1))) + 
  geom_point(
    size = 1
    ) +
  geom_line(
    linewidth = 0.3
    ) + 
  scale_color_brewer(type = "qual") +
  # geom_vline(xintercept = benchmark1, linetype="solid", 
  #            color = "#bdbdbd", linewidth=1, alpha = 0.5) +
  scale_x_continuous("bechmark to remove low-density hexagons", 
         transform = "reverse") + 
  ylab("MSE") +
  ggtitle("(c)") +
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12, 
            angle=90),
        plot.title = element_text(size = 12))
```

>>>>

```{r}
#| label: hexbin-regular-scurve1
## hexagon binning to have regular hexagons
hb_obj_scurve1 <- hex_binning(
  data = umap_scurve_scaled, 
  bin1 = 7, 
  r2 = r2)

a1_1 <- calc_bins_y(
  bin1 = 7, 
  r2 = r2
)$a1

@@

```{r}
#| label: hexbin-regular-scurve2
## hexagon binning to have regular hexagons
hb_obj_scurve2 <- hex_binning(
  data = umap_scurve_scaled, 
  bin1 = 11, 
  r2 = r2)

a1_2 <- calc_bins_y(
  bin1 = 11, 
  r2 = r2
  )$a1

@@

```{r}
#| label: hexbin-regular-scurve3
## hexagon binning to have regular hexagons
hb_obj_scurve3 <- hex_binning(
  data = umap_scurve_scaled, 
  bin1 = 17, 
  r2 = r2)

a1_3 <- calc_bins_y(
  bin1 = 17, 
  r2 = r2
)$a1

@@

effective_bin2_scurve <- calc_bins_y(
  bin1 = effective_bin1_scurve, 
  r2 = r2)$bin2

scurve_model <- fit_highd_model(
  training_data = training_data_scurve,
  emb_df = umap_scurve_scaled,
  bin1 = effective_bin1_scurve,
  r2 = r2,
  is_bin_centroid = TRUE,
  is_rm_lwd_hex = FALSE,
  col_start_highd = "x"
)

@@

<!--To generate errors for different total number of bins-->
```{r}
#| label: bins-scurve

## To initialize benchmark values to remove low density hexagons
benchmark_rm_hex_vec <- append(seq(0, 0.99, by=0.1), c(benchmark1, 0.99))

@@
